---
title: "Descriptive Statistics"
subtitle:  Felix & Mai-Britt , University of Potsdam
date: "15.03 January 2023"
output:
  html_document:
    theme: cosmo
    toc: yes
    toc_float: true
  html_notebook: 
    theme: journal
    toc: true
    toc_float: true
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
fontsize: 12pt
---


# Descriptive Statistics

## Libraries

```{r}
library(readr)
library(ggplot2)

```


## Read in dataset

- Loading our tidy dataset
```{r}
#ap_emi_dev_cl
AP_emi<- read_delim("/Users/maibrittberghofer/Desktop/Master/Module/Dataanalysis/Final Project Dataset/ap_emi_dev_cl.csv", 
    delim = ";",  escape_double = FALSE, trim_ws = TRUE)
#ap_sector_emi_dev_cl
AP_sec <- read_delim("/Users/maibrittberghofer/Desktop/Master/Module/Dataanalysis/Final Project Dataset/ap_sector_emi_dev_cl.csv", 
    delim = ";",  escape_double = FALSE, trim_ws = TRUE)

#emi_ghg_class_region
GHG_emi <- read_csv("/Users/maibrittberghofer/Desktop/Master/Module/Dataanalysis/Final Project Dataset/emi_ghg_class_region.csv")

# emi_sector_ghg
GHG_sector = read_csv("/Users/maibrittberghofer/Desktop/Master/Module/Dataanalysis/Final Project Dataset/emi_sector_ghg.csv")

```
## Visualization


### GHG Emissions by sector 

#### Sector& Development status
```{r}

sector2=GHG_sector[-(which(GHG_sector$`country class`==0)),]
ggplot(data=sector2)+geom_col(aes(x=sector2$`country class`, y=sector2$emissions, fill=sector2$system_stage))+ggtitle("Greenhouse Gas Emissions by Sector", subtitle = "Comparison of Industrialized Countries and Developing Countries")+ylab("GHG Emissions [kton substance/year]")+xlab("Country Class")+scale_fill_discrete(name = "Food System Stage")


```



- Generally there are higher GHG emissions by the food sector emitted by developing countries than be industrialized countries. This could be explained by the fact that generally there are more developing countries (164), than industrialised(59)
- Generally independent of the development status of the country, the highest emissions come due to the processing of food. In developing countries, the highest source for GHG emissions is the LULUC (Land-Use; Land-Use-Change). Whereas in industrialsed countries the highest emissions are in other forms of food processing. Examples of this could be factory farming.


#### Sector & Region 

```{r}
ggplot()+geom_col(aes(x=GHG_sector$region, y=GHG_sector$emissions, fill=GHG_sector$system_stage))+ggtitle("Greenhouse Gas Emissions by Sector", subtitle = "Comparison of different regions")+ylab("GHG Emissions [kton substance/year]")+xlab("Region [IM24_sh]")+scale_fill_discrete(name = "Food System Stage")+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```
- The highest emittants are China, Brazil, India+ and Indonesia+


#### Sector, Emissions and Substance

```{r}
ggplot()+geom_col(aes(x=GHG_sector$substance, y=GHG_sector$emissions, fill=GHG_sector$system_stage))+ggtitle("Greenhouse Gas Emissions by Sector", subtitle = "Comparison of different substances. ")+ylab("GHG Emissions [kton substance/year]")+xlab("Substance")+scale_fill_discrete(name = "Food System Stage")

```
- GWP100 describes the global Warmimg Potential  within the next 100 years

#### Sector, Emissions and Substance

